---
title: "p8105_hw1"
output: github_document
date: "2022-09-23"
---

# Problem 1 

```{r code}
library(tidyverse)

library(dplyr)
```

# Description of Data and Mean of Flipper
```{r}
data("penguins",package = "palmerpenguins")
```

```{r}
nrow(penguins)

ncol(penguins)

mean(pull(penguins,flipper_length_mm),na.rm = TRUE)
```
In this dataset there are 344 rows and 8 columns. Each row represents an individual penguin, it's species type, island, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex (m/f) and year. The mean flipper length is 200.9151 mm. 


#Scatter plot# 

```{r}

myplot2 = 
  ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm,col = species)) + geom_point() 

myplot2

ggsave("myplot2.pdf",myplot2)
```

# Problem 2 

# Creating a new  dataframe

```{r}
third_df = tibble(
  norm = rnorm(10),
  logical = norm > 0, 
  vec_char = c("one","two","three","two","one","one","two","one","two","three"),
  vec_fac = factor (c("one","two","three","one","two","three","one","one","two","three"),
                    levels = c("one", "two", "three" ))
  
)
```

# Taking the means of each variable 

```{r}

mean(pull(third_df,norm))
mean(pull(third_df,logical))
mean(pull(third_df,vec_char))
mean(pull(third_df,vec_fac))

```

Why can do logic: 
 0,1 linear regression, mean of the vector 
5 -> 1 
5 -> 0 

Why it won't do factor/char? 

R doesn't want to do this because it doesn't know how to accutly discribe the length amount difference between these groups...?

proportion of people that had a true value )

#Using as.numeric for logic,char and factor 

```{r}
mean(as.numeric(pull(third_df,logical)))
```
Get the same mean for logic, makes sense! 

```{r}
mean(as.numeric(pull(third_df,vec_char)))
```

```{r}
mean(as.numeric(pull(third_df,vec_fac)))
```
Still won't do the character. Succesfully does logic and vec_fac. 
