---
title: "p8105_hw1"
output: github_document
date: "2022-09-23"
---

# Problem 1 

```{r code}
library(tidyverse)

library(dplyr)
```

# Description of Data 
```{r}
data("penguins",package = "palmerpenguins")
```

```{r}
nrow(penguins)

view(penguins)
```
In this dataset there are 344 rows and 8 columns. Each row represents an individual penguin, it's species type, island, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex (m/f) and year. 

# Find the mean of flipper_length 

```{r}
mean(penguins$flipper_length_mm)
```

```{r}

mean(pull(penguins,flipper_length_mm),na.rm = TRUE)
```

#Scatter plot# 

```{r}
myplot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + geom_point() 

ggsave("myplot2.pdf",myplot)
  
```

# Problem 2 

# Creating a new  dataframe
```{r}
third_df = tibble(
  norm = rnorm(10),
  logical = norm > 0, 
  vec_char = c("one","two","three","two","one","one","two","one","two","three"),
  vec_fac = factor (c("one","two","three","one","two","three","one","one","two","three"),levels = c("one", "two", "three" ))
  
)
```

```{r}

```


# Taking the mean of dateframe

```{r}
mean(third_df$norm)
```
-0.4410941

```{r}
mean(third_df$logical)

```
0.3 
(don't need to write this, 0,1 linear regression, mean of the vector 
5 -> 1 
5 -> 0 

proportion of people that had a true value )

```{r}
mean(third_df$vec_char)
mean(pull(third_df,vec_char))


```
0

```{r}
mean(third_df$vec_fac)
```

#Trying to use pull 

```{r}
library(tidyverse)


library(dplyr)
```


```{r}
#mean(pull(third_df,vec_fac))
```


```{r}

as.numeric(pull(third_df,vec_fac))

mean(as.numeric(pull(third_df,vec_fac)))

```

