---
title: "p8105_hw1"
output: github_document
date: "2022-09-23"
---

# Problem 1 

```{r code}
library(tidyverse)

library(dplyr)
```

# Description of Penguins Data and Mean 
```{r}
data("penguins",package = "palmerpenguins")

```

```{r}
nrow(penguins)

ncol(penguins)

mean(pull(penguins,flipper_length_mm),na.rm = TRUE)
```
In the dataset `penguins` there are *344 rows* and *8 columns*. Each row represents a penguin's  species type, island location, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex (m/f) and year. For this dataset the mean flipper length is *200.9151 mm*. 


# Create a Scatterplot 

```{r}

myplot2 = 
  ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm,col = species)) + geom_point() 

myplot2

ggsave("myplot2.pdf",myplot2)
```

# Problem 2 

# Creating a New Dataframe

```{r}
third_df = tibble(
  norm = rnorm(10),
  logical = norm > 0, 
  vec_char = c("one","two","three","two","one","one","two","one","two","three"),
  vec_fac = factor (c("one","two","three","one","two","three","one","one","two","three"),
                    levels = c("one", "two", "three" ))
  
)
```

# Taking Means of Each Variable 

```{r}

mean(pull(third_df,norm))
mean(pull(third_df,logical))
mean(pull(third_df,vec_char))
mean(pull(third_df,vec_fac))

```

Simply pulling the column from the dataset and getting the mean was succesful for the *normally distributed variable* and *logical variable*. The reason it worked for the normally distributed variable is straight forward because it has numeric values. However, for the logical variable, it was still able to calculate a mean because it labeled the character variables as either a '0' or '1', so this value allows us to interpret it as a proportion (had the true value). 

Unlike *vector variable* or a *factor variable* which R does not give values of 'O' or '1' so when trying to calculate the mean of a character value, it will only say "NA". 

# Converting variables  

```{r}
mean(as.numeric(pull(third_df,logical)))
```
Get the same mean for logic, makes sense! 

```{r}
mean(as.numeric(pull(third_df,vec_char)))
```

```{r}
mean(as.numeric(pull(third_df,vec_fac)))
```

_How do I not show the output. Is it already doing that?_

When we convert these variables into numeric values. The R code is able to do it succesfully for only *logic variable* and the *vector variable*. The same method is used to explain what's happening to the logic variable *above*. 
However, it can not do it for a character variable because it doesn't know the diffence between the groups, unlike the vector which tells it how to rank it. 



R doesn't want to do this because it doesn't know how to acutely discribe the length difference between these three levels. 


Still won't do the character. Succesfully does logic and vec_fac. 
